When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about individual SVs

INSERT FIGURE 2 HERE

```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

  print(sca_plot)

@@

@@

INSERT FIGURE 3 HERE

```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}

  #print(plot_h3a)

>>>>

INSERT FIGURE 2 HERE
<!--
```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

  include_graphics(here("06_Paper", "Stage 2", "Figures", "sca-plot.png"))

@@

Figure\ \@ref(fig:nfc-sv) shows a scatterplot of SVs per *n*-back level, colored depending on the participant's NFC score.
There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across *n*-back levels.
At the same time, there is a subtle separation of SVs across *n*-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
Specifically, $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` participants had an absolute preference for 1-back, $n=$`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])` for 2-back, $n=$`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])` for 3-back, and $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` for 4-back.
There were $n=$`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))` participants who did not have an absolute preference for any *n*-back level, i.e. none of their SVs was 1.

INSERT FIGURE 3 HERE
<!--
```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level. Each dot indicates a participant, the colours indicate their Need for Cognition score. $N=116$. There is a horizontal jitter of 0.4 and a vertical jitter of 0.05.", fig.pos="H"}

  include_graphics(here("06_Paper", "Stage 2", "Figures", "nfc-sv.png"))

@@

INSERT FIGURE 4 HERE
<!--
```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}

  include_graphics(here("06_Paper", "Stage 2", "Figures", "h3a-plot.png"))
